Visualization and analysis of probability distributions of large temporal data

### 2021-11-19 Rmd/04-gracsr.Rmd
fig reference caption remove quote

(ref:summary-plot-wpd) "Summary plots for three (a) and five (b) clusters from WPD approach showing the $\wpd$ values of each customers across *hod*, *moy*, and *wnwd* through a parallel coordinate plot. P-1 and P-2 groups correspond to Q-1 and Q-2, respectively. Cluster P-3 is subdivided into Q-3, Q-4, and Q-5. P-1 (customers 16, 18) is distinguished by high $\wpd$ on *wnwd* values. P-2 has lower $\wpd$ than *moy* and *wnwd* for *hod*. P-3 operates in the opposite way as P-2, with larger $\wpd$ for *hod* in comparison to *moy* and *wnwd*. For the $5$ cluster solution, this group is divided into Q-3, Q-4, Q-5, which are distinct due to their different relative significance of *moy* and *wnwd*."

>>>>

(ref:summary-plot-wpd) Summary plots for three (a) and five (b) clusters from WPD approach showing the $\wpd$ values of each customers across *hod*, *moy*, and *wnwd* through a parallel coordinate plot. P-1 and P-2 groups correspond to Q-1 and Q-2, respectively. Cluster P-3 is subdivided into Q-3, Q-4, and Q-5. P-1 (customers 16, 18) is distinguished by high $\wpd$ on *wnwd* values. P-2 has lower $\wpd$ than *moy* and *wnwd* for *hod*. P-3 operates in the opposite way as P-2, with larger $\wpd$ for *hod* in comparison to *moy* and *wnwd*. For the $5$ cluster solution, this group is divided into Q-3, Q-4, Q-5, which are distinct due to their different relative significance of *moy* and *wnwd*.
